### 2024-08-17 paper.tex
m

\section{Finding the Springer fiber at a Slodowy slice}
\par Fix any \(X \in \mathcal{N}\).
As we have fixed \(X\), we now write \(A_{a, b} := A_{X, a, b}\).
Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be a Jordan basis for \(X\).
For convenience we define \(e_{i0} := 0\); now we may express the fact that \((e_{ij})\) is a Jordan basis by writing \(\forall i. Xe_{ij} = e_{i,j - 1}\).
\par In this section we find the irreducible components of
\[\pi^{-1}(X) \cong V := \{(A_{a, b}, U) : \forall i. \; A_{a, b} U_{i + 1} \subseteq U_i\}.\]
\par For \(1 \leq w \leq k\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\)), define 
\[V_{w,r} := \{(A_{a, b}, U) \in V : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'} \}.\]

@@

Define the linear map \(Q_{wr} : \mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) by:

@@

    \item For \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\)
    \item For \(j \leq \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\)
    \item If \(r \neq 0\), then \(e_{w,\lambda_w} \mapsto f_1'\), and blah.

@@

We begin by choosing a new basis to simplify things by setting \(a = 0\) (that is, we will work with the matrices of the form \(A_{X',0,b'}\)).
Here is the new basis.
For \(i \neq w\), take the chain beginning with \(e_{i,\lambda_i}\).
Then take the chain beginning with \(e_{w,r - 1}\).

% Since \(\pi^{-1}(X) \cong \pi^{-1}(AXA^{-1})\) for any invertible \(A\), we will assume that \(X\) is in Jordan normal form.
Let \(f_1, ..., f_n\) be the standard basis for \(\mathbb{C}^n\), with \(A_{X, a, b} f_i = f_{i + 1}\).

>>>>

\section{Strategy and setup for finding the irreducible components of a Springer fiber at a Slodowy slice}
\par Fix any \(X \in \mathcal{N}\).
As we have fixed \(X\), we now write \(A_{a, b} := A_{X, a, b}\).
Let \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\) be a Jordan basis for \(X\).
For convenience we define \(e_{i0} := 0\); now we may express the fact that \((e_{ij})\) is a Jordan basis by writing \(\forall i. Xe_{ij} = e_{i,j - 1}\).
\par In this section we find the irreducible components of
\[\pi^{-1}(X) \cong V := \{(A_{a, b}, U) : \forall i. \; A_{a, b} U_{i + 1} \subseteq U_i\}.\]
\par For \(1 \leq w \leq k\) and \(0 \leq r \leq \lambda_w\) (note that we allow \(r = 0\)), define 
\[V_{w,r} := \{(A_{a, b}, U) \in V : \exists P \in \GL_{m}. \; \exists b'. \; (P^{-1}, I_n) A_{a, b} (P, I_n) = A_{e_{wr}, b'} \}.\]

@@

Define the linear map \(Q_{wr} : \mathbb{C}^{m' + n'} \to \mathbb{C}^{m + n}\) by:

@@

    \item For all \(i\), \(e_{ij}' \mapsto e_{ij}\).
    \item For \(j = 1, ..., r\), \(f_{n + j}' \mapsto e_{w,(\lambda_w - r) + j}\).
    \item For \(j = 1, ..., n\), \(f_j' \mapsto f_j + e_{w, (\lambda_w - r) - n + j}\).

@@

% The inverse map \(Q_{wr}^{-1} : \mathbb{C}^{m + n} \to \mathbb{C}^{m' + n'}\) is
% \begin{itemize}
%     \item For all \(i \neq w\), \(e_{ij} \mapsto e_{ij}'\).
%     \item For \(j = 1, ..., \lambda_w - r\), \(e_{wj} \mapsto e_{wj}'\).
%     \item For \(j = 1, ..., r\), \(e_{wj} \mapsto f'_{n + j}\).
%     \item For \(j = 1, ..., n\), \(f_j \mapsto f'_j - e_{w,\lambda_w - n + r}\)
% \end{itemize}
Observe that conjugation by \(Q_{wr}\) maps \(U_{wr}\) to \(U'_{wr}\), and conjugation by \(Q_{wr}^{-1}\) maps \(U'_{wr}\) to \(U_{wr}\).
We conclude that \(U_{wr} \cong U_{wr}'\); so to find the irreducible components of \(U_{wr}\) we just need to find the irreducible components of \(U_{wr}'\).
To clear the context, which is rather cluttered by now, and to avoid writing primes everywhere, we move to a new section.

\section{Finding the irreducible components of \(U\)}
Let \(X\) be nilpotent of shape \(\lambda\), etc.
Start fresh finding irreducible components of \(U_{w0}\).

\section{Finding the irreducible components of a springer fiber at a slodowy slice}
Apply things from the previous two sections, and conclude.
